Solution-aware vs global ReLU selection: \\ partial MILP strikes back for DNN verification

### 2025-01-28 CAV 2025 TODO/Comparison.tex
push

\section{Global Ranking Functions}

@@

First, we adapt from the BaB-SR \cite{BaB} and FSB \cite{FSB} functions (replacing the symbols from the original paper with those used in our paper.), selecting a node to branch on for BaB, global ranking (GR) functions to select nodes for pMILP. Intuitively, we extract the scoring $s_{SR}$ and $s_{FSB}$ from both BaB-SR and FSB, as the BaB bounding step is not adapted for pMILP. They both work by backpropagating gradients vectors $\bm{\lambda}$ from the neurons under consideration in layer $n$, back to neurons to be potentially selected. To do so, they consider the rate of $\ReLU(\bm{u}_k)$ to be 
$r(\bm{u}_k)=\frac{\max(0,\UB(\bm{u}_k))}{\max(0,\UB(\bm{u}_k))-\min(0,\LB(\bm{u}_k))} \in [0,1]$.

@@

We call {\em global rankings} (GR) such functions $s_{FSB},s_{SR}$  because they score ReLUs as accuratly as possible, considering that they do not have access to the solution $sol(a),sol(b)$ values. This analysis already hints at our novel ranking function, that will be solution-aware to be more accurate.

>>>>

\section{Global Scoring Functions}

@@

First, we adapt from the BaB-SR \cite{BaB} and FSB \cite{FSB} functions (replacing the symbols from the original paper with those used in our paper.), selecting a node to branch on for BaB, {\em  global scoring} (GS) functions to select nodes for pMILP. Intuitively, we extract the scoring $s_{SR}$ and $s_{FSB}$ from both BaB-SR and FSB, as the BaB bounding step is not adapted for pMILP. They both work by backpropagating gradients vectors $\bm{\lambda}$ from the neurons under consideration in layer $n$, back to neurons to be potentially selected. To do so, they consider the rate of $\ReLU(\bm{u}_k)$ to be 
$r(\bm{u}_k)=\frac{\max(0,\UB(\bm{u}_k))}{\max(0,\UB(\bm{u}_k))-\min(0,\LB(\bm{u}_k))} \in [0,1]$.

@@

We call {\em global scoring} (GS) such functions $s_{FSB},s_{SR}$  because they score ReLUs as accuratly as possible, considering that they do not have access to the solution $sol(a),sol(b)$ values. This analysis already hints at our novel ranking function, that will be solution-aware to be more accurate.
